### 2014-04-24 article.tex
Add a Conclusions section to P2.

\section{Conclusions}
Conclusions to go here\ldots

>>>>

The MIKE SHE/MIKE 11 model performed well at reproducing the observerations from the validation period after having been calibrated.
It had a slight tendency to overestimate the discharge in summer when the discharge was at its lowest, and underestimate it in winter when it was at its highest.
According the the guidelines put forward by \textcite{henriksen2008assessment}, it performs excellently.
Under a scenario of Low emissions up to 2050, the model predicts that the average monthly discharge at both of the measuring stations will be broadly unchanged.
Under Medium and High emissions scenarios up to 2050, the model predicts that the average monthly discharge at both of the measuring stations will be higher by about 10\% over the course of the year, with the biggest change in winter.
